%
%Academic CV LaTeX Template
% Author: Poojitha
% LinkedIn: https://www.linkedin.com/in/poojitha-gaddam/
% License: MIT
%
% For errors, suggestions, or improvements, please contact:
% Email: poojithagaddam2006@gmail.com
%



\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}

% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}

% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{1em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

\begin{document}
\headerfontiii

% Header
\begin{center}
    {\Huge\textbf{GADDAM POOJITHA}}
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    +91-9441231375 | \href{mailto:poojithagaddam2006@gmail.com}{poojithagaddam2006@gmail.com} | 
    }
\end{center}
\vspace{-6mm}

\begin{center}
    \small{
    \socialicon{\faLinkedin} \href{https://www.linkedin.com/in/poojitha-gaddam}{poojitha-gaddam} | 
    \socialicon{\faGithub} \href{https://github.com/Poojitha-90}{Poojitha-90}  
   
    }
\end{center}
\vspace{-6mm}
\begin{center}
    \small{Hyderabad, Telangana - 500043, India}
\end{center}

\vspace{-4mm}

\section{\textbf{Objective}}
\vspace{1mm}
\small{
Seeking a challenging position in the software development field to leverage my expertise in full-stack development, data structures, and algorithmic problem-solving. Aiming to contribute to innovative projects at the intersection of scalable web technologies and real-world application development in areas such as enterprise software, cloud computing, and AI-driven solutions.


}
\vspace{-2mm}
\section{\textbf{Experience}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
  \resumeSubheading
    {Internship at Electrical Sub-Station}{Pochampally, India}
    {Intern – Substation Operations and Maintenance}{May 2024 – June 2024}
    \resumeItemListStart
      \item Observed and assisted in the operation and maintenance of electrical equipment including transformers and circuit breakers.
      \item Gained hands-on experience in monitoring power distribution and understanding substation control systems.
      \item Supported daily load analysis, maintenance scheduling, and fault detection processes.
      \item Maintained documentation and safety compliance records under supervision of engineers.
    \resumeItemListEnd 
\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Education}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{Institute of Aeronautical Engineering}{Dundigal,India}
{Bachelors of Technology in Electronics and Communication}{2023 - 2027}
\resumeItemListStart
\item GPA: 8.8/10.0
\resumeItemListEnd

\resumeSubheading
{Sri Chaitanya Junior College }{Hyderabad,India}
{MPC }{2023}
\resumeItemListStart
\item Grade: 9.45\%
\resumeItemListEnd

\resumeSubheading
{St.Peters Grammar School}{Hyderabad,India}
{X Class}{2021}
\resumeItemListStart
\item GPA: 10/10
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Projects}}
\vspace{-1.5mm}

\resumeProject
  {Ultrasonic Radar System}
  
  {June 2025}
 
\resumeItemListStart
  \item Designed and built a radar system using ultrasonic sensors to detect object proximity and direction.
  \item Integrated Arduino with a servo motor to provide 180-degree scanning coverage.
  \item Visualized distance and direction of obstacles on a real-time radar interface.
  \item Applied embedded programming techniques for sensor control and signal processing.
\resumeItemListEnd

\resumeProject
  {Intern Edge – Web-Based Internship Toolkit}
  
  {May 2025}
  
\resumeItemListStart
  \item Developed a responsive web platform for internship preparation with categorized resources.
  \item Implemented dynamic sections for resume tips, interview Q&A, and platform links using JavaScript.
  \item Designed intuitive UI/UX using HTML and CSS for student-friendly navigation.
  \item Ensured compatibility across devices using media queries and modern layouts.
\resumeItemListEnd

\resumeProject
  {Own AI Agent-AI Powered Personal Assistant}
  
  {February 2025}
  
\resumeItemListStart
  \item Created a virtual assistant capable of answering contextual queries using LangChain and OpenAI APIs.
  \item Built a Flask web app interface for text input/output and voice command support.
  \item Integrated task management, web search, and information summarization features.
  \item Applied natural language processing to provide human-like responses.
\resumeItemListEnd

\resumeProject
  {Gas Leakage Detection System}
  
  {November 2024}
  
\resumeItemListStart
  \item Built a gas leakage detection system using MQ sensors for real-time monitoring.
  \item Triggered alarms and sent SMS alerts via GSM module on detecting hazardous gas levels.
  \item Programmed microcontroller logic for continuous data acquisition and threshold-based alerts.
  \item Designed the system to be cost-effective, reliable, and suitable for household use.
\resumeItemListEnd
\section{\textbf{Skills}}
\vspace{-0.4mm}
\resumeHeadingSkillStart
  \resumeSubItem{Languages:}
    {Python, Java, Python with Data Science, HTML/CSS}
  \resumeSubItem{Frameworks \& Tools:}
    {Flask, AutoCAD, Xilinx Vivado}
  \resumeSubItem{Concepts:}
    {Object-Oriented Programming (OOP), Data Structures, IoT, PCB Design}
  \resumeSubItem{Version Control:}
    {Git, GitHub}
  \resumeSubItem{IDEs:}
    {VS Code,Arudino IDE,NI Multisim}
  \resumeSubItem{Soft Skills:}
    {Project Management, Team Leadership, Technical Documentation}
\resumeHeadingSkillEnd
\section{\textbf{Certifications}}
\vspace{-0.2mm}
\resumeSubHeadingListStart

\resumePOR{}{\href{https://drive.google.com/file/d/1nHKslZrNwzSrWAYQNinGTahyx2LDEzK2/view?usp=drivesdk}{
\textbf{Python for Beginners – Great Learning}
}}

\resumePOR{}{\href{https://drive.google.com/file/d/1Pwu1lKi8mOuRiKi65hXx4bBliRC2WNtI/view?usp=drivesdk}{\textbf{Career Edge – Young Professional TCS iON}}}

\resumePOR{}{\href{https://drive.google.com/file/d/1Iv74fb7ZkQUT1DpgFyMsbZLGlNDNQbXW/view?usp=drivesdk}{\textbf{Introduction to Soft Skills – TCS iON}}}


\resumePOR{}{\href{https://drive.google.com/file/d/1siL_gXbMJuWd4V4N5Y12NFFKdG3jwW7G/view?usp=drivesdk}{\textbf{Core Java Guide: Key Features \& OOP – Udemy}}}

\resumePOR{}{\href{https://drive.google.com/file/d/1alLX24-eepFoqD6J7M_JHgOAP9FNC6jC/view?usp=drivesdk}{\textbf{Java Programming Fundamentals – Infosys Springboard}}}

\resumePOR{}{\href{https://drive.google.com/file/d/1ZtLKgEtR4e89ptdqPrbV6FZyyumC3cBF/view?usp=drivesdk}{\textbf{Python with Data Science – Infosys Springboard}}}

\resumePOR{}{\href{https://drive.google.com/file/d/1VrypP2dq5VgGrfpC9z_75PsfIbcSg9AX/view?usp=drivesdk}{\textbf{Python Programming – HackerRank}}}

\resumeSubHeadingListEnd
\vspace{-6mm}
\section{\textbf{Additional Information}}
\vspace{-0.4mm}
\small{
\textbf{Languages:} English (Fluent), Telugu (Native), Hindi (Conversational)

\textbf{Interests:} Public Speaking, Problem Solving, UI Designing, Blogging
}
\vspace{-4mm}
\end{document}